A community-maintained standard library of population genetic simulations

### 2019-12-19 popSimManu.tex
text edits and figure updates

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\linewidth]{display_items/Figure1.pdf}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the PopSim catalog contains all information
within individual species. Information within the species level is shown here
for \emph{Homo sapiens} only. We see that \emph{H. sapiens} is associated
with a default generation time and mutation rate,
a representation of the physical genome, and two genetic maps. Also shown is a
subset of the demographic models currently implemented. \textbf{B.} Caching
and automated download of genetic maps. \textbf{C.} Example code to specify
and simulate models using \stdpopsim via the API (top) or
command-line interface (bottom). \textbf{D.} Simulation output
is a tree sequence file that can
be manipulated and analyzed with \tskit.}
\label{fig:cartoon}
\end{center}
\end{figure}

@@

\section*{Acknowledgements}
We thank the Probabilistic Modeling in Genomics conference organizers with making this collaboration possible.
Early on in the project we were helped by many people including XXXXXX.
CCK and KEL were funded under NIH Award R35GM119856.
JRA and ADK were funded under NIH Award R01GM117241.
TJS and RNG were funded under NIH Award R01GM127348.
ALG and DRS were funded under NIH award R00HG008696
ND and AS were supported in part by NIH Awards R01HG010346 and R35GM127070.
FR and GG were supported by a Villum Young Investigator award (project no.~00025300).
DODV is funded by a UC MEXUS-CONACYT Collaborative Grant and a DGAPA-PAPIIT grant (PAPIIT-IA200620).
JK is supported by the Robertson Foundation.

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.7\linewidth]{display_items/Figure1.pdf}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the \stdpopsim catalog contains all model simulation information
within individual species (expanded information shown here for \emph{Homo sapiens} only). 
Each species is associated with a representation of the physical genome, and one or more genetic maps and demographic models.
Dotted lines indicate that only a subset of these categories is shown. \textbf{B.} Example code to specify
and simulate models using \stdpopsim via the API (top) or\textbf{C.} through a command line interface.}
\label{fig:cartoon}
\end{center}
\end{figure}

@@

\section*{Acknowledgements}
We thank the Probabilistic Modeling in Genomics conference organizers with making this collaboration possible.
Early on in the project we were helped by many people including XXXXXX.
CCK and KEL were funded under NIH Award R35GM119856.
JRA and ADK were funded under NIH Award R01GM117241.
TJS and RNG were funded under NIH Award R01GM127348.
ND and AS were supported in part by NIH Awards R01HG010346 and R35GM127070.
FR and GG were supported by a Villum Young Investigator award (project no.~00025300).
DODV is funded by a UC MEXUS-CONACYT Collaborative Grant and a DGAPA-PAPIIT grant (PAPIIT-IA200620).
JK is supported by the Robertson Foundation.
